COG-ED Manuscript

### 2022-06-13 06_Paper/COG-ED/Manuscript.Rmd
corrected formal errors

  include_graphics(here("99_Thinktank", "Other", "Paradigm_Scheme.png"))

@@

Data collection and analysis will not be performed blind to the conditions of the experiments.
We will exclude the data of a participant from all analyses, if the participant states that they did not follow the instructions, if the investigator notes that the participant misunderstood the instructions, or if the participant withdraws their consent.
No data will be replaced.
We aim to conduct all analysis as described in Westbrook et al.[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate[@Macmillan1990].
Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before[@Whelan2008; @Berger2021].
Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively[@Lachaud2011].
Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in an MLM, because RT on the latter is longer due to more cautious behavior[@Dutilh2012; @Houtman2012].
To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results[@Singmann2019].<br>
*Manipulation check.*
Declining performance will be investigated by calculating an rmANOVA with six paired contrasts comparing *d'* between two levels of 1- to 4-back at a time.
Another rmANOVA with six paired contrasts will be computed to compare the median RT between two levels of 1- to 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1- to 4-back at a time.<br>
*Subjective values.*
For each effort discounting round, the SV of the fixed level will be calculated by adding or subtracting the last adjustment of 0.02\ € from the last monetary value of the flexible level, depending on the participant's last choice, and dividing this value by 2\ €.
This yields an SV between 0 and 1 for the fixed compared with the flexible level, while the SV of the flexible level is 1.
The closer the SV of the fixed level is to 0, the stronger the preference for the flexible level.
All SVs of each level will be averaged to compute one "global" SV for each level.
An rmANOVA with four different contrasts will be computed to investigate the association of SVs and the *n*-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
Depending on whether the linear or one of the other three contrasts fits the curve best, we will apply a linear or nonlinear multi-level model in the next step, respectively.

@@

The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r printnum(mean(data_quest[,"age"], na.rm = TRUE))`$ ($SD=`r printnum(sd(data_quest[,"age"], na.rm = TRUE))`$)\ years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
The results showed increases in subjective and objective task load measures with higher *n*-back level.
Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which can be considered preliminary proof-of-concept, as this phenomenon can only emerge in this version of the paradigm.
The LMM revealed *n*-back level as a reliable predictor of SV, even after controlling for declining task performance (*d’* and median RT).
The specification curve analysis showed that this pattern was true for all 63 pipelines.
Finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
All results are detailed in the Supplementary Material.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3a_rmanova,
  caption = "Main effects and interaction of NFC group and n-back level on subjective values",
  note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3b_rmanova,
  caption = "Main effects and interaction of NFC group and n-back level on NASA-TLX scores",
  note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

>>>>

  include_graphics(here("06_Paper", "Inkscape Figures", "Paradigm_Scheme.png"))

@@

Data collection and analysis will not be performed blind to the conditions of the experiments.
We will exclude the data of a participant from all analyses, if the participant states that they did not follow the instructions, if the investigator notes that the participant misunderstood the instructions, or if the participant withdraws their consent.
No data will be replaced.
We aim to conduct all analysis as described in Westbrook et al.[-@Westbrook2013], but the level of detail was not always sufficient, so there might be deviations regarding data cleaning and degrees of freedom.
The performance measure *d'* will be computed as the difference of the *z*-transformed hit rate and the *z*-transformed false alarm rate[@Macmillan1990].
Reaction time (RT) data will be trimmed by excluding all trials with responses faster than 100\ ms, as the relevant cognitive processes cannot have been completed before[@Whelan2008; @Berger2021].
Aggregated RT values will be described using the median and the median of absolute deviation ($MAD$) as robust estimates of center and variability, respectively[@Lachaud2011].
Error- and post-error trials will be excluded in repeated measures analyses of variance (rmANOVA) and controlled for in an MLM, because RT on the latter is longer due to more cautious behavior[@Dutilh2012; @Houtman2012].
To test our hypotheses, we will perform a series of rmANOVAs and an MLM with orthogonal sum-to-zero contrasts in order to meaningfully interpret results[@Singmann2019].

*Manipulation check.*
Declining performance will be investigated by calculating an rmANOVA with six paired contrasts comparing *d'* between two levels of 1- to 4-back at a time.
Another rmANOVA with six paired contrasts will be computed to compare the median RT between two levels of 1- to 4-back at a time.
To investigate changes in NASA-TLX ratings, six rmANOVAs will be computed, one for each NASA-TLX subscale, and each with six paired contrasts comparing the ratings between two levels of 1- to 4-back at a time.

*Subjective values.*
For each effort discounting round, the SV of the fixed level will be calculated by adding or subtracting the last adjustment of 0.02\ € from the last monetary value of the flexible level, depending on the participant's last choice, and dividing this value by 2\ €.
This yields an SV between 0 and 1 for the fixed compared with the flexible level, while the SV of the flexible level is 1.
The closer the SV of the fixed level is to 0, the stronger the preference for the flexible level.
All SVs of each level will be averaged to compute one "global" SV for each level.
An rmANOVA with four different contrasts will be computed to investigate the association of SVs and the *n*-back levels: Declining linear (3,1,-1,-3), ascending quadratic (-1,1,1,-1), declining logistic (3,2,-2,-3), and positively skewed normal (1,2,-1,-2).
Depending on whether the linear or one of the other three contrasts fits the curve best, we will apply a linear or nonlinear multi-level model in the next step, respectively.

@@

The sample of the pilot study consisted of $N=`r length(setindex)-1`$ participants (`r round((table(data_quest$gender)[2]/(length(setindex)-1))*100, digits = 1)`% female, $M=`r printnum(mean(data_quest[,"age"], na.rm = TRUE))`$ ($SD=`r printnum(sd(data_quest[,"age"], na.rm = TRUE))`$)\ years old).
One participant's data was removed because they misunderstood the instruction.
Due to a technical error the subjective task load data of one participant was incomplete, so the hypotheses involving the NASA Task Load Index were analyzed with $n=`r length(setindex)-2`$ data sets.
The results showed increases in subjective and objective task load measures with higher *n*-back level.
Importantly, SVs were lower for higher *n*-back levels, but not different between 1- and 2-back, which shows that the easiest level is not universally preferred.
The LMM revealed *n*-back level as a reliable predictor of SV, even after controlling for declining task performance (*d’* and median RT).
The specification curve analysis showed that this pattern was true for all 63 pipelines.
Finally, while the $AxAUC$ value did not predict any amount of variance in individual NFC scores, the $AUC$ of NASA-TLX scores did.
All results are detailed in the Supplementary Material.

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3a_rmanova,
  caption = "Main effects and interaction of NFC group and n-back level on subjective values",
  note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H",
  font_size = "footnotesize"
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis3b_rmanova,
  caption = "Main effects and interaction of NFC group and n-back level on NASA-TLX scores",
  note = "NFC = Need for Cognition, Sum Sq = sum of squares, $df$ = degrees of freedom, $F$ = $F$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H",
  font_size = "footnotesize")
```
